Exploring the conformational dynamics of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation

### 2013-09-05 writedown/npt-neq/alanine.tex
update according Christof's comment
add abstract. revise for submission

\begin{abstract}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
  \caption{Schematic plot of the nonequilibrium temperature control scheme.
    The white area is the region characterized by Hamiltonian dynamics without the direct action of an external thermostat.
    The gray area is the region where the external thermostat is used in order to keep the target temperature.
    $R_{ex}$ denotes the size of the Hamiltonian dynamics region, which
    is a sphere at the center of the box.
    The whole system is subject to the periodic boundary conditions. }
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/c-2.eps}}
  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-begin-1.eps}
  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-end-1.eps}
  \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
    (a): the
    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    action of a constant EF of 1~V/nm. The darker color
    indicates higher probability.}
  \label{fig:tmp4}
\end{figure}

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
range of conformations changes when the external EF is applied.
For instance, the population of conformation $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast the change is, and the relations to the 
the EF. 
First, we calculate the probability of being in a certain conformation range,
defined as:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Second,
we study the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
Here the time interval $\Delta t$ should be small enough comparing with the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be linearly approximated.
In the meanwhile,  $\Delta t$ should also be  large enough comparing with
the timestep of MD integrator, 
so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
estimated with good statistical accuracy.
See also the discussions in Ref.~\cite{schuette2011markov}.
$F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
into $I$ at time $t$. A positive value indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
If the resulting reduced process 
is time-reversible, then it is obvious that
$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
the irreversibility of the reduced process on
$\{A_1, A_2, B_1, B_2, C\}$.
% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
% in Eq.~\eqref{eqn:tmp7} by the finite difference,
% then calculate the joint probabilities on
% the right-hand-side from the molecular trajectories.
% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
% preferable although the statistical uncertainty of measuring the joint probabilities
% is higher. In practice,
% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
In the case of oscillatory EF, the net probability flux is also highly oscillatory,
thus it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
this expresses the average over time of the effects of the EF on the conformation of the molecule.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-npt.eps}
  \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$.
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integral, for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ in units of $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line represents the strength of the
    external EF, while the solid line represents the dipole
    moments. The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-rdf.eps}
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-hbond.eps}
  \caption{The solvent structure around the alanine dipeptide.  Plot
    (a): the radial distribution function (RDF) between the
    $\alpha$-carbon and the center-of-mass (COM) of the water molecules at
    $t = 0$, 10, 100 and 1000~ps.  Plot (b): the number of hydrogen
    bonds formed between the alanine and water, and between two water
    molecules.  The number of hydrogen bonds between two water
    molecules is normalized by the number of water molecules in the
    system.}
  \label{fig:tmp7a}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% solvent effect
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We study the solvent effect on the alanine dipeptide in the presence of the EF by investigating
the radial distribution function between $\alpha$-carbon and the
center-of-mass (COM) of the water molecules
(see Fig.~\ref{fig:tmp7a}). The average, relative position of the COM of water molecules measured w.r.t.~the alanine does not change significantly as a function of time (within the statistical error). Plot (b) of
Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
alanine and water molecules, and between two water molecules. We see that the
number hydrogen bonds remains almost the as the EF is turned on,
although molecular dipoles tend to align with the direction of the EF (result
not shown). 
The EF-induced solvent effect on the alanine is also counted by calculating the
difference of the water-alanine electrostatic interaction 
between systems without and with the EF.
The energy difference is found to be $-19.1$~~kJ/mol that is
comparable to the electrostatic energy associated to the dipole of the alanine itself.
Therefore, we conclude that the solvation structure around the
alanine does not change significantly or contribute significantly in determining the conformational dynamics of the alanine under the action of EF.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-conv.eps}
  \caption{Testing the finite-size effect of the Hamiltonian dynamics and thermostated region.
    Probabilities of different ranges of conformations are presented as a function of time.
    See the text for more details.
  }
  \label{fig:tmp7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF:
    the dipole moment (a) and
    orientation order parameter (b) of alanine dipeptide as a
    function of time. In plot (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF with turning on
    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period
    10~ps, while the green line is for a period of 40~ps and the blue for 200~ps.}
  \label{fig:tmp8}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig.ala/fig-meta-mode2-2000.eps}
  \caption{ The probability of being in a certain range of conformations for
    periodically oscillatory EF. Different periods,
    i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
    probability of being in a certain conformation range $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
    blue line: $I = B_1$, the pink line: $I = B_2$ and the light blue
    line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
    simulations of time 1000~ps are presented, while for $T=200$~ps,
    nonequilibrium simulations of time 3200~ps is presented.  }
  \label{fig:tmp9}
\end{figure}

@@

  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-5.eps}\\

@@

  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-5.eps}\\

@@

  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-5.eps}\\

@@

\bibliography{ref}{}
\bibliographystyle{unsrt}

>>>>

\begin{abstract}
  In this paper, we investigate the conformational dynamics of alanine
  dipeptide under an external electric field (EF) by the
  nonequilibrium molecular dynamics (MD) simulation, which enables us
  to calculate the nonequilibrium physical properties that are not
  available for traditional equilibrium MD simulation.  We study both
  the constant and oscillatory EF cases, and discuss the way to
  implement the temperature control in the nonequilibrium MD
  simulation, which removes the irrelevant thermal effect of the EF
  from the system. In the constant EF case, different time-scales are
  discovered in the conformational, dipole moment, and orientational
  dynamics. Moreover, we prove that the solvent structure only
  marginally changes when the external EF is switched on.  In the
  oscillatory EF case, the conformational changes are shown to be as
  strong as constant EF case, and non-trivial nonequilibrium
  conformational circulations are presented by calculating the
  integrated net probability fluxes.
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{thermostat.eps}
  \caption{Schematic plot of the nonequilibrium temperature control scheme.
    The white area is the region characterized by Hamiltonian dynamics without the direct action of an external thermostat.
    The gray area is the region where the external thermostat is used in order to keep the target temperature.
    $R_{ex}$ denotes the size of the Hamiltonian dynamics region, which
    is a sphere at the center of the box.
    The whole system is subject to the periodic boundary conditions. }
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
  \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
  \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
  \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
    (a): the
    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    action of a constant EF of 1~V/nm. The darker color
    indicates higher probability.}
  \label{fig:tmp4}
\end{figure}

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
range of conformations changes when the external EF is applied.
For instance, the population of conformation $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast the change is, and the relations to the 
the EF. 
First, we calculate the probability of being in a certain conformation range,
defined as:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the probability is time dependent, being an observable in nonequilibrium situation.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Second,
we study the net probability flux from conformation $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
Here the time interval $\Delta t$ should be small enough comparing with the
time scale of conformational dynamics,
so that the changes in the conformation probabilities
can be linearly approximated.
In the meanwhile,  $\Delta t$ should also be  large enough comparing with
the timestep of MD integrator, 
so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
estimated with good statistical accuracy.
See also the discussions in Ref.~\cite{schuette2011markov}.
$F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
into $I$ at time $t$. A positive value indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
% If the resulting reduced process 
% is time-reversible, then it is obvious that
% $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
% the irreversibility of the reduced process on
% $\{A_1, A_2, B_1, B_2, C\}$.
% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
% in Eq.~\eqref{eqn:tmp7} by the finite difference,
% then calculate the joint probabilities on
% the right-hand-side from the molecular trajectories.
% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
% preferable although the statistical uncertainty of measuring the joint probabilities
% is higher. In practice,
% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
In the case of oscillatory EF, the net probability flux is also highly oscillatory,
thus it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
this expresses the average over time of the effects of the EF on the conformation of the molecule.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-npt.eps}
  \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $A_1$,
    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
    to $C$.
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integral, for the constant EF case.
    The warm-up time is $t_{warm} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ in units of $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

@@

\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the molecular dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line represents the strength of the
    external EF, while the solid line represents the dipole
    moments. The left vertical axis is for the dipole moment, while
    the right is for the orientational order parameter.
  }
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig-rdf.eps}
  \includegraphics[width=0.48\textwidth]{fig-hbond.eps}
  \caption{The solvent structure around the alanine dipeptide.  Plot
    (a): the radial distribution function (RDF) between the
    $\alpha$-carbon and the center-of-mass (COM) of the water molecules at
    $t = 0$, 10, 100 and 1000~ps.  Plot (b): the number of hydrogen
    bonds formed between the alanine and water, and between two water
    molecules.  The number of hydrogen bonds between two water
    molecules is normalized by the number of water molecules in the
    system.}
  \label{fig:tmp7a}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% solvent effect
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We study the solvent effect on the alanine dipeptide in the presence of the EF by investigating
the radial distribution function between $\alpha$-carbon and the
center-of-mass (COM) of the water molecules
(see Fig.~\ref{fig:tmp7a}). The average, relative position of the COM of water molecules measured w.r.t.~the alanine does not change significantly as a function of time (within the statistical error). Plot (b) of
Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
alanine and water molecules, and between two water molecules. We see that the
number hydrogen bonds remains almost the as the EF is turned on,
although molecular dipoles tend to align with the direction of the EF (result
not shown). 
The EF-induced solvent effect on the alanine is also counted by calculating the
difference of the water-alanine electrostatic interaction 
between systems without and with the EF.
The energy difference is found to be $-19.1$~~kJ/mol that is
comparable to the electrostatic energy associated to the dipole of the alanine itself.
Therefore, we conclude that the solvation structure around the
alanine does not change significantly or contribute significantly in determining the conformational dynamics of the alanine under the action of EF.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig-meta-conv.eps}
  \caption{Testing the finite-size effect of the Hamiltonian dynamics and thermostated region.
    Probabilities of different ranges of conformations are presented as a function of time.
    See the text for more details.
  }
  \label{fig:tmp7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
  \caption{Illustration of the effect of the oscillatory EF:
    the dipole moment (a) and
    orientation order parameter (b) of alanine dipeptide as a
    function of time. In plot (a),
    only the $x$-component of the dipole moment is
    shown. The black line refers to the static EF with turning on
    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period
    10~ps, while the green line is for a period of 40~ps and the blue for 200~ps.}
  \label{fig:tmp8}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
  \caption{ The probability of being in a certain range of conformations for
    periodically oscillatory EF. Different periods,
    i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
    probability of being in a certain conformation range $I$, which is
    denoted by $P_I$ in this paper, is plotted by colored lines against
    time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
    blue line: $I = B_1$, the pink line: $I = B_2$ and the light blue
    line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
    simulations of time 1000~ps are presented, while for $T=200$~ps,
    nonequilibrium simulations of time 3200~ps is presented.  }
  \label{fig:tmp9}
\end{figure}

@@

  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\

@@

  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\

@@

  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\

@@

\begin{thebibliography}{10}

\bibitem{bohr2000microwave}
Henrik Bohr and Jakob Bohr.
\newblock Microwave-enhanced folding and denaturation of globular proteins.
\newblock {\em Physical Review E}, 61(4):4310, 2000.

\bibitem{bohr2000microwave-1}
Henrik Bohr and Jakob Bohr.
\newblock Microwave enhanced kinetics observed in ord studies of a protein.
\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.

\bibitem{dePomerai2000cell}
David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
  Candido.
\newblock Cell biology: Non-thermal heat-shock response to microwaves.
\newblock {\em Nature}, 405:417--418, 2000.
